### 2014-05-09 tex/main-body-text.tex

\subsection*{Analysis of coasta California steelhead} 
To evaluate the preformance and computational efficiency of {\sc flock}  we used a published 
dataset from \citet{Garzaetal_norcal} comprised of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci.  {\sc flock} was run six times using the default setting for all run parameters 
\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. The non-admixture, uncorrelated allele frequency model implemented in {\sc structure}
was run with six iterations of a 50,000 sweep burn-in followed by 150,000 sweep sample 
from the posterior of \textit{k} from 2 to 6. To facilitate the comparison of the two programs,
the program {\sc clump} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program Distruct \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

>>>>

\subsection*{Analysis of coastal California steelhead} 
To evaluate the preformance and computational efficiency of {\sc flock}  we used a published 
dataset from \citet{Garzaetal_norcal} comprised of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci.  {\sc flock} was run six times using the default setting for all run parameters

\textit{(initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0)} for values of \textit{k} from 2 to 6. The stopping point of 
\textit{k}=6 was chosen because four consecutive runs with 0 length plateaus were 
produced. The non-admixture, uncorrelated allele frequency model implemented in {\sc structure}
was run with six iterations of a 50,000 sweep burn-in followed by 150,000 sweep sample 
from the posterior of \textit{k} from 2 to 6. To facilitate the comparison of the two programs,
the program {\sc clump} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program Distruct \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.
